---
title: "ESM 262 week 3"
author: "Edaysi Bucio"
date: "19 de abril de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Download packages and data base

```{r}

library(tidyverse)

heights <- read.csv("heights.csv")

foo <- read_csv("a,b,c
1,2,3
4,5,6")

bar <- read_csv("1,2,3\n4,5,6", dol_names = c("x", "y", "z"))

baz <- parse_logical(c("TRUE", "FALSE", "NA", "bozo")) #Makes logical arguments? Conversion 
problems(baz)

#Parsel characters
parse_double("1.23e10")

parse_double("1,23", locale = locale(decimal_mark = ","))

charToRaw("Hadley")

x1 <- "El Ni\xf1o was particularly bad this year"
x1

parse_character(x1, locale = locale(encoding = "Latin1"))

parse_date("01/02/15", "%m/%d/%y")


############################################################## Excercise 2

challenge <- read_csv(readr_example("challenge.csv")) #Problem

challenge <- read_csv(readr_example("challenge.csv"), #Problem
                      col_types = cols(
                        x = col_double(),
                        y = col_logical()
                      ))

challenge <- read_csv(readr_example("challenge.csv"), #Problem
                      col_types = cols(
                        x = col_double(),
                        y = col_character()
                      )) #With a character im forcing to not do other interpretation of the colum, that is why I'm not getting the error

tail(challenge)

challenge <- read_csv(readr_example("challenge.csv"), #Problem
                      col_types = cols(
                        x = col_double(),
                        y = col_date()
                      )) #By telling R that Y is in date format, R can look into this colum as dates




```


How to read a csv file that is in text?
```{r}

?read_delim

gaz_raw <- read_delim("CA_Features_20190301.txt","|")
View(gaz_raw)


```






Notes

Link: https://r4ds.had.co.nz/data-import.html

Pase_double = gives cientific notation you need to write the number as parse_double("1.23e10"")
locale = put in a specific location. Creates a local specification
Locale can be apply to the entire data frame 
parse_numbes ---> Goes to look and find numbers, or de closest one when you give numbers with decimals. 

charToRaw("Hadley") --> Represents chunks of bits. Sexadecimals are use to talk about bits
