---
title: "Assignment_packages"
author: "Edaysi Bucio"
date: "4 de junio de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)

```

#Data
Database source: https://climateknowledgeportal.worldbank.org/download-data 
```{r}

TempMX <- read_csv("temperatureMX.csv")
PreciMX <- read_csv("precipitationMX.csv")

```


1. At least two different functions that summarize climate data in some way (your choice - it could be finding a trend, or finding extremes; or even simply mean winter precipitation)

1.1 First function. I want to find the highest temperatures registered from 1901 to 2016 in Mexico. With this information I can look if there is a trend in warmer days increasing or decreasing over time. 

```{r}

#Data frame
#TempMX_df <- TempMX 

#Function
Climate_average <- function(TempMX_df, plot = TRUE){
    Hot_days <- TempMX_df %>%
    group_by(Year) %>%
    filter(Temperature == max(Temperature)) %>%
    ungroup() 
    if(plot == TRUE) {
Hot_days_plot <- ggplot(TempMX_df, aes(x = Year, y = Temperature)) +
    geom_point(size = 1.5) + 
  ggtitle("Maximum Temperature in Celsius From Mexico 1901-2016") +
  labs(y="Anually Maximum Temperature (degrees C)", x="Year")+
  theme_classic() + 
  geom_smooth(method="lm")
    print(Hot_days_plot)
    }
    return(Hot_days)
  } #First function that summarize climate trends

(x <- Climate_average(TempMX_df = TempMX, plot = TRUE))

#Overall questions: Am I adding the multi-dimensional arrays in this function? 



```


1.2. My second function will look at an average precipitation per year from 1901 to 2016 in Mexico. Afterwards, I can calculate a measure of impact between hot days and changes in precipitation and potential impacts on agriculture or water availability in the country. 

```{r}

#Data frame
#PreciMX_df <- PreciMX

#Function
Rainfall_average <- function(PreciMX_df, plot = TRUE){
  Precip_average <- PreciMX_df %>%
    group_by(Year) %>%
    summarise(Average = mean(Rainfall)) %>%
    ungroup() 
    if(plot == TRUE) {
Rainfall_average_plot <- ggplot(PreciMX_df, aes(x = Year, y = Rainfall)) +
    geom_point(size = 1.5) + 
  ggtitle("Average Rainfall From Mexico 1901-2016") +
  labs(y="Average Rainfall", x="Year")+
  theme_classic() + 
  geom_smooth(method="lm")
  print(Rainfall_average_plot)
    }
  return(Precip_average) 
  } #First function that summarize climate trends

(r <-  Rainfall_average(PreciMX_df = PreciMX, plot = TRUE)) 



```



2. At least two functions that calculate some measure of impact (you can really make these us) -so for example you could create a function that computes a heat stress index based on air temperature with parameters that vary with for different species; or a function that estimates water supply from precipitation with parameters that vary to reflect water storage .you can make something up just as long as its somewhat sensible.

2.1. Measure of impact: I'm calculating if there is a relationship between warmer days and drought years

```{r}

#Assuming that the previous database have sea surface temperature (Temperature), I will identified El Niño years and potential impacts on marine species such as squid and tuna. Thus, I will create a function that computes ENSO index based on SST and impacts on different marine species. 

Nino_impacts <- function(El_nino_df){
    Hot_days <- El_nino_df %>%
    group_by(Year) %>%
    filter(Temperature == max(Temperature))
    ungroup()   
      {
y <- x %>%
    select(Temperature)
    }
Squid_impacts <- y
if(Squid_impacts < 24) 
  print("North distribution")
  
tuna_impacts <- y
if(tuna_impacts > 24)  #The condition has length > 1 and only the first element will be usedError: unexpected '}' in "if(tuna_impacts > 24) }"
  print("South distribution")
} 
   #First function that summarize climate trends


(climate_impacts <- Squid_impacts(El_nino_df = TempMX))





```

2.2  Measure of impact: I will create a function that estimates water supply from precipitation with parameters that vary to reflect water storage. Those parameters are hot days and average precipitation

```{r}

```

3. One function that estimates the costs of impacts
```{r}

```

