---
title: "Homework 1"
author: "Edaysi Bucio"
date: "3 de mayo de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(DBI)
library(RSQLite)
library(sqldf)
library(dbplyr)

```

#Connect Rmd SQL chunk to SQLite database
```{r}


db <- dbConnect(RSQLite::SQLite(), dbname = "database.db")
src_dbi(db)

db2 <- dbConnect(SQLite(), "database.db")
dbListTables(db)

#Problem: I do not have tables while creating the db file. I get stuck in here

```

#1. ##  1. What are the 10 most-frequently-occuring land uses (in descending order)? 
```{r}


```


##  1. What are the 10 most-frequently-occuring land uses (in descending order)? 
Hint: Load the UseCodes into a separate tibble, then join it to the parcels tibble.

```{sql connection=db}

#parcels_raw %>%
  select(LandUse) %>%
  filter(!is.na(LandUse)) %>% #Especifying that I want the top 10 #Factors that occurs the most I need to drop other
  count(LandUse, sort = TRUE) %>%
  print(n = Inf)


SELECT LandUse, personal FROM Person


```

## 2. How many acres are in agricultural preserves? 
Assume agricultural preserves are indicated by non-NA values for AgPres.
Answer: 549,563.4 acres
```{sql connection=db}

preserves <- parcels_raw2 %>%
  select(acreage, agpress) %>%
  filter(!is.na(acreage)) %>%
  filter(!is.na(agpress))

sum(as.numeric(preserves$acreage)) #Sum all acres from agricultural preserves


```


## 3. What is the mean net assessed value per acre of the entire county? 
Answer: The average net value per acre is $34,202.63


```{r}

Total_acre <- parcels_raw2 %>%
  select(acreage)

Total_value <- parcels_raw2 %>%
  select(NetAv) 

Mean_val <- sum(Total_value)/sum(Total_acre)#Find the total land value of the county and divided by the total land /acreage

Mean_val #Show the value


```

## 4. What is the total net assessed value of all non-taxable parcels? 
Answer: The total net assessed value of non-taxable parcels is $1,093,026,091 


```{r}

NonT <- parcels_raw2 %>%
  group_by(ntcode, NetAv) %>%
  filter(!is.na(ntcode)) %>%
  summarize(total_val = sum(NetAv, na.rm = TRUE))

Net_Value <- sum(NonT$total_val)
Net_Value


# 1,093,026,091   

```

## 5. What are the 10 largest property holders, by acreage? 
Use the complete mailing address for tax statements as a proxy for the parcel owner. Ignore parcels where either component of the address is NA.

#The tenth row should be PO Box 338, Santa Ynez, with about 9,200 acres.

```{r}

parcels_raw2 %>%
  group_by(Address1, acreage) %>%
  drop_na() %>% #Change fct_lump by group_by and use summarize to add all of the acress by owner 
  count(Address1, acreage, sort = TRUE)

parcels_raw2 %>%
  group_by(Address1, Adress2) %>%
  summarize(total_val = sum(net_val, na.rm = TRUE))

#Combine address 1 and address 2 

#View(Situs_acreage)

flights %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay, na.rm = TRUE))

result2 <- parcels %>%
  group_by(mail_addr1, mail_addr2) %>%
  summarize(total_val = sum(net_val, na.rm = TRUE))


```

## 6. What are the 10 largest property holders, by net assessed value?

```{r}

parcels_raw2 %>%
  select(site2, land_value) %>%
  drop_na() %>%
  mutate(site2 = fct_lump(site2, n = 10)) %>% 
  count(land_value, site2, sort = TRUE) %>%
  group_by(land_value)
 
  

```

