---
title: "Homework 3"
author: "Edaysi Bucio"
date: "24 de mayo de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

autopower = function(V, m, A, cdrag=0.3, crolling=0.015,pair=1.2,g=9.8) {
  P = crolling*m*g*V + 1/2*A*pair*cdrag*V**3
  return(P)
}

```

## Assignment indications
- What if we design new highways that have lower rolling coefficients where we reduce the rolling coefficient by 50%

- Alternatively, we implement a policy that reduce the mean speed from 100 km/h to 80 km/h (still with 10% standard deviation)

- Calculate the mean power for both (assuming the same car probabilities above) and sampling from speeeds with 10% standard deviation = assume a normal distribution

- Put your function in a *.R file Use an Rmarkdown document to do your analysis and summarize result at the end

Submit both R file (function) and Rmarkdown that does the analysis as usual using a git link


#Function
```{r}

Speeds_Function100 = function(speeds100) {
  result = speeds100**0.28
  return(result)
}


Speeds_Function80 = function(speeds80) {
  result = speeds80**0.28
  return(result)
}

```


#Step 1

```{r}

# Generate sample speeds from a distribution
# Step 1  create data frame to store results 
nsample = 100000
speeds100 = rnorm(mean=100*0.028, sd=10, n=nsample) #Speed in m/s
results100 = data.frame(speed=speeds100, power=NA)
head(results100)


speeds80 = rnorm(mean=80*0.28, sd=10, n=nsample) #Speed in m/s
results80 = data.frame(speed=speeds80, power=NA)
head(results80)

#Yep, I got negative speeds

```

#Plot results. Example of plot
```{r}

#100 km/h or 27.7 m/s
results100$power = autopower(V=speeds100, A=25, m=20000)
# ALWAYS look at your results to make sure it make sense
ggplot(results100, aes(speeds100, power/1000))+geom_point()+labs(x="speed in m/s", y="power in kW")


#80 km/h or 22.2 m/s
results80$power = autopower(V=speeds80, A=25, m=20000)
# ALWAYS look at your results to make sure it make sense
ggplot(results80, aes(speeds80, power/1000))+geom_point()+labs(x="speed in m/s", y="power in kW")


```

# Sampling different cars
```{r}

possible_cars = data.frame(mass=c(31000,45000,38000), area = c(25,30,22))

# first look at how results vary for a given speed say 100km/hr
speed_base1 = 100 * 0.28
speed_base2 = 80 * 0.28

# because I have one mass and area for each car there will be a unique speed
#Speed 100 km/h
possible_cars$power = autopower(V=speed_base, A = possible_cars$area, m=possible_cars$area)
                         
ggplot(possible_cars, aes(x=mass, y=power, fill=mass))+geom_col()+labs(y="Power W", x="Mass (kg)")

#Speed 80km/h
possible_cars$power = autopower(V=speed_base2, A = possible_cars$area, m=possible_cars$area)
                         
ggplot(possible_cars, aes(x=mass, y=power, fill=mass))+geom_col()+labs(y="Power W", x="Mass (kg)")



```



# Calculate the mean power for both (assuming the same car probabilities above) and sampling from speeeds with 10% standard deviation = assume a normal distribution.

Mean power with a speed of 100km/hr = 3.331
Mean power with a speed of 80km/hr = 3.332

```{r}

# Estimate average power use given a range of speeds and different probabilities of particular cars

possible_cars$prob = c(0.4, 0.4, 0.2)



# Normal distribution of speeds with mean 100km/hr and with 80km/hr
m = log(100*0.28)
m2 = log(80*0.28)
nsample = 100000
speeds = rnorm(mean=m, sd=0.1*m, nsample)
summary(speeds) 

speeds2 = rnorm(mean=m2, sd=0.1*m, nsample)
summary(speeds2) 


```

# Calculate the mean power for both (assuming the same car probabilities above) and sampling from speeeds with 10% standard deviation = assume a normal distribution.

Mean power with a speed of 100km/hr = 3.331
Mean power with a speed of 80km/hr = 3.332
