---
title: "Homework 1"
author: "Edaysi Bucio"
date: "3 de mayo de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readr)
library(dplyr)

```

## Packages and database
```{r}


parcels_raw <- read_csv("Santa_Barbara_County_parcels_2011.csv",
 col_types = cols(.default = col_character()))


View(parcels_raw)


```


## Import and tidy 

**Read the parcels data as-is (all columns; no automatic type conversion) into a parcels_raw tibble.**
```{r}

parcels_raw2 <- select(parcels_raw,
                   apn = APN,
                   site1 = Situs1,
                   site2 = Situs2, 
                   acreage = Acreage,
                   code = UseCode,
                   ntcode = NonTaxCode,
                   agpress = AgPres,
                   land_value = LandValue,
                   NetImpr = Net_Impr,
                   NetAV = Net_AV,
                   Address1 = M_Address1,
                   Adress2 = M_Address2)

#Double with decimals
#Integer complete numbers

```

** Convert the parcels columns to the appropriate type. Convert any placeholders for unknown data to NA**
```{r}

#Individually setting the columns 

#parcels2$apn = parse_character(parcels2$apn)

parcels_raw2 <-
  transmute(parcels_raw,
    apn         = parse_character(APN, na = "Unknown"),
    site1       = parse_character(Situs1, na = "Unknown"),
    site2       = parse_character(Situs2, na = "Unknown"),
    acreage     = parse_number(Acreage,na = "Unknown"),
    code        = parse_character(UseCode, na = "Unknown"),
    ntcode      = parse_character(NonTaxCode, na = "Unknown"),
    agpress     = parse_character(AgPres, na = "Unknown"),
    land_value  = parse_number(LandValue, na = "Unkown"),
    NetImpr     = parse_number(Net_Impr, na = "Unknown"),
    NetAv       = parse_number(Net_AV, na = "Unknown"),
    Address1    = parse_character(M_Address1, na = "Unknown"),
    Adress2     = parse_character(M_Address1, na = "Unknown")
  )


```

## Write the parcels tibble to a CSV file (using "|" as a delimiter).
```{r}

write_delim(parcels_raw,
  "parcels.csv",
  delim = "|",
  na = ""
)


```


##  1. What are the 10 most-frequently-occuring land uses (in descending order)? 
Hint: Load the UseCodes into a separate tibble, then join it to the parcels tibble.

```{r}

parcels_raw %>%
  select(LandUse) %>%
  filter(!is.na(LandUse)) %>% #Especifying that I want the top 10 #Factors that occurs the most I need to drop other
  count(LandUse, sort = TRUE) %>%
  print(n = Inf)


#parcels_raw2 %>%
 # group_by(Land) ##Connect USe code and landuse #Join the two databases
#count()


```

## 2. How many acres are in agricultural preserves? 
Assume agricultural preserves are indicated by non-NA values for AgPres.
Answer: 549,563.4 acres
```{r}

preserves <- parcels_raw2 %>%
  select(acreage, agpress) %>%
  filter(!is.na(acreage)) %>%
  filter(!is.na(agpress))

sum(as.numeric(preserves$acreage)) #Sum all acres from agricultural preserves


```


## 3. What is the mean net assessed value per acre of the entire county? 
Answer: The average net value per acre is $34,202.63


```{r}

Total_acre <- parcels_raw2 %>%
  select(acreage)

Total_value <- parcels_raw2 %>%
  select(NetAv) 

Mean_val <- sum(Total_value)/sum(Total_acre)#Find the total land value of the county and divided by the total land /acreage

Mean_val #Show the value


```

## 4. What is the total net assessed value of all non-taxable parcels? 
Answer: The total net assessed value of non-taxable parcels is $1,093,026,091 


```{r}

NonT <- parcels_raw2 %>%
  group_by(ntcode, NetAv) %>%
  filter(!is.na(ntcode)) %>%
  summarize(total_val = sum(NetAv, na.rm = TRUE))

Net_Value <- sum(NonT$total_val)
Net_Value


# 1,093,026,091   

```

## 5. What are the 10 largest property holders, by acreage? 
Use the complete mailing address for tax statements as a proxy for the parcel owner. Ignore parcels where either component of the address is NA.

#The tenth row should be PO Box 338, Santa Ynez, with about 9,200 acres.

```{r}

parcels_raw2 %>%
  group_by(Address1, acreage) %>%
  drop_na() %>% #Change fct_lump by group_by and use summarize to add all of the acress by owner 
  count(Address1, acreage, sort = TRUE)

parcels_raw2 %>%
  group_by(Address1, Adress2) %>%
  summarize(total_val = sum(net_val, na.rm = TRUE))

#Combine address 1 and address 2 

#View(Situs_acreage)

flights %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay, na.rm = TRUE))

result2 <- parcels %>%
  group_by(mail_addr1, mail_addr2) %>%
  summarize(total_val = sum(net_val, na.rm = TRUE))


```

## 6. What are the 10 largest property holders, by net assessed value?

```{r}

parcels_raw2 %>%
  select(site2, land_value) %>%
  drop_na() %>%
  mutate(site2 = fct_lump(site2, n = 10)) %>% 
  count(land_value, site2, sort = TRUE) %>%
  group_by(land_value)
 
  

```

