---
title: "Homework 4. Fisu Function"
author: "Edaysi Bucio"
date: "29 de mayo de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)

```

## Indications
Write a function that takes as input

- A table that has prices for different fish
- A table that has the number caught for each fish YES
species for each location
- Each location is in a different column
- Each fish is in a different row 

#Input
```{r}

#Creating vectors
fish = c("grouper","mullet","tuna","puffer","snapper")
price = c("20","15","18","10","14")
catch = c("150","180","220","200","92")
location = c("location 1","location 2","location 3","location 4","location 5")

as.numeric(catch)
as.numeric(price)

# Creating my Fish data frame
Fish_df <- crossing(fish, location) %>%
  mutate(catch = runif(min = 0, max = 100, n = nrow(.))) %>%
  mutate(price = runif(min = 0, max = 100, n = nrow(.)))

Fish_df

```


#Function

Function output will be:
- most frequently caught fish in each location
- total revenue for each location
- total fisheries revenue sum 
- if user requests it graph of revenue by location and total revenue (as text)

Place your function in an *.R file Make a package that contains this function

Generate some example data for your function; and show how this is created and used in an R markdown document Submit package and Rmarkdown as usual as a git link on gauchospace.

```{r Function}

#The function output should always include the total revenue as one of the elements in the list.

Fish_function <- function(Fish_df) {
  fish = as.character(Fish_df)
  calc_fish_revenue = catch**price
  calc_mostfrecuent_caught = fish**location
  calc_total_revenue = sum(calc_fish_revenue)
  return(list(num = calc_fish_revenue, calc_mostfrecuent_caught = calc_mostfrecuent_caught, calc_total_revenue = calc_total_revenue))                         
}


```

## Retuning values
- Most frequently caught fish in each location

Answer:

# Location 1 = snapper with 97.77 kilograms
# Location 2 = grouper with 84.86 kilograms
# Location 3 = tunna with 90.05 kilograms
# Location 4 = mullet with 70.91 kilograms 
# Location 5 = puffer with 96.72 kilograms
```{r}

(Most_caught <- Fish_df %>%
  group_by(location, fish) %>%
  summarize(max_catch = max(catch)))

(Most_caught <- Fish_df %>%
  group_by(location) %>%
  summarize(Max_catch = max(catch), fish_specie = mode(fish)))


```

## Total revenue for each location

```{r}

Total_revenue <- Fish_df %>%
  group_by(location) %>%
  summarise(revenue = sum(price))

Total_revenue

```

## Total fisheries revenue sum 
```{r}
Revenue_sum <- Fish_df %>%
  summarise(revenue = sum(price))

Revenue_sum


```


