---
title: "Homework 4. Fisu Function"
author: "Edaysi Bucio"
date: "29 de mayo de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```

## Indications
Write a function that takes as input

- A table that has prices for different fish
- A table that has the number caught for each fish YES
species for each location
- Each location is in a different column
- Each fish is in a different row 

#Input
```{r}

#Creating vectors
fish = c("grouper","mullet","tuna","puffer","snapper")
price = c("20","15","18","10","14")
catch = c("150","180","220","200","92")
location = c("location 1","location 2","location 3","location 4","location 5")

# Creating my Fish data frame
Fish_df <- crossing(fish, location) %>%
  mutate(catch = runif(min = 0, max = 100, n = nrow(.)))

Fish_df

```


#Function

Function output will be:
- most frequently caught fish in each location
- total revenue for each location **OPTIONAL?**
- total fisheries revenue sum 
- if user requests it graph of revenue by location and total revenue (as text)

Place your function in an *.R file Make a package that contains this function

Generate some example data for your function; and show how this is created and used in an R markdown document Submit package and Rmarkdown as usual as a git link on gauchospace.

```{r Function}

#The function output should always include the total revenue as one of the elements in the list.

Fish_function = function(Fish_df) {
  fish = as.character(Fish_df)
  calc_fish_revenue = fish**price
  calc_mostfrecuent_caught = fish**location
  calc_total_revenue = sum(calc_fish_revenue)
  return(list(num = calc_fish_revenue, calc_mostfrecuent_caught = calc_mostfrecuent_caught, calc_mostfrecuent_caught = calc_mostfrecuent_caught))                         
}



#Class example


## function (species) 
## {
##     species = as.factor(species)
##     tmp = (summary(species)/sum(summary(species)))^2
##     diversity = sum(tmp)
##     return(diversity)
## }



##function (species) 
## {
##     species = as.factor(species)
##     tmp = (summary(species)/sum(summary(species)))^2
##     diversity = 1 - sum(tmp)
##     nspecies = length(summary(species))
##     tmp = which.max(summary(species))
##     dominant = names(summary(species)[tmp])
##     return(list(num = nspecies, simpson = diversity, dominant = dominant))
## }

```

## Retuning values
```{r}

Fish_function$calc_fish_revenue



```

