---
title: "Homework 1"
author: "Edaysi Bucio"
date: "3 de mayo de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(DBI)
library(RSQLite)
library(sqldf)
library(dbplyr)
library(tidyverse)

```
####### Old code from homework 1 #############################################

```{r}

parcels_raw <- read_csv("Santa_Barbara_County_parcels_2011.csv",
 col_types = cols(.default = col_character()))

```

## Import and tidy 

**Read the parcels data as-is (all columns; no automatic type conversion) into a parcels_raw tibble.**
```{r}

parcels_raw2 <- select(parcels_raw,
                   apn = APN,
                   site1 = Situs1,
                   site2 = Situs2, 
                   acreage = Acreage,
                   code = UseCode,
                   ntcode = NonTaxCode,
                   agpress = AgPres,
                   land_value = LandValue,
                   NetImpr = Net_Impr,
                   NetAV = Net_AV,
                   Address1 = M_Address1,
                   Adress2 = M_Address2)

```

** Convert the parcels columns to the appropriate type. Convert any placeholders for unknown data to NA**
```{r}

parcels_raw2 <-
  transmute(parcels_raw,
    apn         = parse_character(APN, na = "Unknown"),
    site1       = parse_character(Situs1, na = "Unknown"),
    site2       = parse_character(Situs2, na = "Unknown"),
    acreage     = parse_number(Acreage,na = "Unknown"),
    code        = parse_character(UseCode, na = "Unknown"),
    ntcode      = parse_character(NonTaxCode, na = "Unknown"),
    agpress     = parse_character(AgPres, na = "Unknown"),
    land_value  = parse_number(LandValue, na = "Unkown"),
    NetImpr     = parse_number(Net_Impr, na = "Unknown"),
    NetAv       = parse_number(Net_AV, na = "Unknown"),
    Address1    = parse_character(M_Address1, na = "Unknown"),
    Adress2     = parse_character(M_Address1, na = "Unknown")
  )

View(parcels_raw)

```

####### New code #############################################################

#Connect Rmd SQL chunk to SQLite database
```{r create parcels database}


Parcels <- dbConnect(RSQLite::SQLite(), dbname = "parcels.db") #Creating an empty database. Creating the connection step

dbListTables(Parcels) 

dbWriteTable(conn = Parcels, name = "tableP", value = parcels_raw) #Creating all my data

```

```{r}

OldParcels <- dbConnect(RSQLite::SQLite(), dbname = "parcels.db") 
dbWriteTable(conn = Parcels, name = "tableOrig", value = parcels_raw) 
dbListTables(OldParcels) 



```



```{sql, connection=Parcels}

SELECT * FROM tableP
 
```

#1. ##  1. What are the 10 most-frequently-occuring land uses (in descending order)? 

If you are not sure, use SELECT * FROM tableP to select all the columns, then see which columns are useful for answering the question and switch the * to those column names. #tableP
```{sql, connection=OldParcels}

SELECT DISTINCT Acreage, LandUse
FROM tableOrig
WHERE LandUse IS NOT NULL
GROUP BY LandUse
ORDER BY Acreage DESC


```



## 2. How many acres are in agricultural preserves? 
Answer: 549,563.4 acres

```{sql connection=Parcels}

SELECT sum(acreage)
FROM tableP 
WHERE agpress IS NOT NULL


```


## 3. What is the mean net assessed value per acre of the entire county? 
Answer: The average net value per acre is $34,202.63


```{sql connection=Parcels}

SELECT avg(NetAv)/avg(acreage) 
FROM tableP
WHERE NetAv IS NOT NULL



```

## 4. What is the total net assessed value of all non-taxable parcels? 
Answer: The total net assessed value of non-taxable parcels is $1,093,026,091 


```{sql connection=Parcels}

SELECT sum(NetAv)
FROM tableP 
WHERE Ntcode IS NOT NULL


```

## 5. What are the 10 largest property holders, by acreage? 
Use the complete mailing address for tax statements as a proxy for the parcel owner. Ignore parcels where either component of the address is NA.

#The tenth row should be PO Box 338, Santa Ynez, with about 9,200 acres.

```{sql connection=Parcels}

SELECT DISTINCT Address1, acreage 
FROM tableP 
WHERE Address1 IS NOT NULL
GROUP BY Address1 
ORDER BY acreage DESC;


```

## 6. What are the 10 largest property holders, by net assessed value?
The second row should be 735 Anacapa, SB, at about $190 million.

```{sql connection=Parcels}


SELECT DISTINCT Address1, NetAv 
FROM tableP 
WHERE Address1 IS NOT NULL
GROUP BY Address1 
ORDER BY NetAv DESC;

```

