---
title: "Homework 1"
author: "Edaysi Bucio"
date: "3 de mayo de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(DBI)
library(RSQLite)
library(sqldf)
library(dbplyr)

```
####### Old code from homework 1 #############################################

```{r}

parcels_raw <- read_csv("Santa_Barbara_County_parcels_2011.csv",
 col_types = cols(.default = col_character()))

```

## Import and tidy 

**Read the parcels data as-is (all columns; no automatic type conversion) into a parcels_raw tibble.**
```{r}

parcels_raw2 <- select(parcels_raw,
                   apn = APN,
                   site1 = Situs1,
                   site2 = Situs2, 
                   acreage = Acreage,
                   code = UseCode,
                   ntcode = NonTaxCode,
                   agpress = AgPres,
                   land_value = LandValue,
                   NetImpr = Net_Impr,
                   NetAV = Net_AV,
                   Address1 = M_Address1,
                   Adress2 = M_Address2)

```

** Convert the parcels columns to the appropriate type. Convert any placeholders for unknown data to NA**
```{r}

parcels_raw2 <-
  transmute(parcels_raw,
    apn         = parse_character(APN, na = "Unknown"),
    site1       = parse_character(Situs1, na = "Unknown"),
    site2       = parse_character(Situs2, na = "Unknown"),
    acreage     = parse_number(Acreage,na = "Unknown"),
    code        = parse_character(UseCode, na = "Unknown"),
    ntcode      = parse_character(NonTaxCode, na = "Unknown"),
    agpress     = parse_character(AgPres, na = "Unknown"),
    land_value  = parse_number(LandValue, na = "Unkown"),
    NetImpr     = parse_number(Net_Impr, na = "Unknown"),
    NetAv       = parse_number(Net_AV, na = "Unknown"),
    Address1    = parse_character(M_Address1, na = "Unknown"),
    Adress2     = parse_character(M_Address1, na = "Unknown")
  )

```

####### New code #############################################################

#Connect Rmd SQL chunk to SQLite database
```{r create parcels database}


Parcels <- dbConnect(RSQLite::SQLite(), dbname = "parcels.db") #Creating an empty database. Creating the connection step

src_dbi(Parcels) 
dbListTables(Parcels) #When I'm trying to get the list of tables, it just showed up the name of the dataset, no the name of each table as it is supposed. Not sure if I'm missing a step. 

```

```{sql, connection=db}

SELECT * 
FROM Santa_Barbara_County_parcels_2011

 
```

#1. ##  1. What are the 10 most-frequently-occuring land uses (in descending order)? 
```{sql, connection=db}

SELECT name AS tables FROM Santa_Barbara_County_parcels_2011
WHERE type = 'table'


```


##  1. What are the 10 most-frequently-occuring land uses (in descending order)? 
Hint: Load the UseCodes into a separate tibble, then join it to the parcels tibble.

```{sql connection=db}




SELECT LandUse, personal FROM Person


```

## 2. How many acres are in agricultural preserves? 
Assume agricultural preserves are indicated by non-NA values for AgPres.
Answer: 549,563.4 acres
```{sql connection=db}


```


## 3. What is the mean net assessed value per acre of the entire county? 
Answer: The average net value per acre is $34,202.63


```{r}



```

## 4. What is the total net assessed value of all non-taxable parcels? 
Answer: The total net assessed value of non-taxable parcels is $1,093,026,091 


```{r}

```

## 5. What are the 10 largest property holders, by acreage? 
Use the complete mailing address for tax statements as a proxy for the parcel owner. Ignore parcels where either component of the address is NA.

#The tenth row should be PO Box 338, Santa Ynez, with about 9,200 acres.

```{r}


```

## 6. What are the 10 largest property holders, by net assessed value?

```{r}


```

